A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-06-02 src/paper.tex
WIP: some changes in text

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. Considering the interactions of millions of viewers, the generated data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}.

The conventional remote control (RC) is typically used as a standard medium for viewers to interact with their TVs. However, this medium presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture contextualized viewers' interactions. As a result, the entire group of viewers (e.g., a family) is treated as a single viewer and the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

@@

>>>>

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services and improve audience~\cite{Teixeira2010}.

The conventional remote control (RC) is typically used as the standard medium for viewers to interact with their TVs. However, this medium presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture contextualized viewers' interactions. As a result, the entire group of viewers (e.g., a family) is treated as a single viewer and the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

@@

% In order to support millions of viewers, this architecture was implemented under a cloud based platform
